% -*- root: diplomarbeit.tex -*-
\newpage{}

\begin{thebibliography}{SMAT}
\bibitem[TLD]{TLD} Kalal Z., Mikolajczyk K., Matas J., ``Tracking-Learning-Detection.'', \textit{Pattern Analysis and Machine Intelligence}, IEEE Transactions on (Volume:34 , Issue: 7 ), pages 1409-1422, July 2012.

\bibitem[MFT]{MFT} Kalal Z., Mikolajczyk K., Matas J., ``Forward-Backward Error: Automatic Detection of Tracking Failures.'' \textit{Proc. 20th Int'l Conf. Pattern Recognition}, pages 23-26, 2010.

\bibitem[OPT]{OPT} Lucas B.D., Kanade T., ``An iterative image registration technique with an application to stereo vision.'' \textit{International Joint Conference on Artificial Intelligence}, pages 674-679, 1981.

\bibitem[OCV]{OCV} Bradski G., Kaehler A., ``Learning OpenCV: Computer Vision with the OpenCV Library.''\textit{ O\textquoteright{}Reilly Media, 1st edition}, Oct. 2008.

\bibitem[NCC]{key-5} Lewis J.P., ``Fast normalized cross-crorrelation.'' \textit{Vision Interface. Canadian Image Processing and Pattern Recognition Society}, pages 120-123, 1995.

\bibitem[IIM]{key-6} Viola P., Jones M., ``Rapid object detection using a boosted cascade of simple features.'', \textit{2001 IEEE Computer Society Conference on Computer Vision and Pattern Recognition}, volume 1, pages I\textendash{}511\textendash{}I\textendash{}518, Los Alamitos, CA, USA, Apr. 2001

\bibitem[VID]{key-7} Video Analyse - Therie and practice.

\bibitem[PYR]{key-8} Bouguet J-V, ``Pyramidal Implementation of the Lucas Kanade Feature Tracker : Description of the algorithm.'', \textit{Intel Corporation \textendash{} Microprocessor Research Labs}, 2002.

\bibitem[BAB]{BAB} Blaschko M. B., ``Branch and Bound Strategies for Non-maximal Suppression in Object Detection.'', \textit{volume 6819 of Lecture Notes in Computer Science}, chapter 28, pages 385-398. Springer Berlin Heidelberg, Berlin, Heidelberg, 2011.

\bibitem[OTS]{OTS} Yilmaz A., Javed O., Shah M., ``Object tracking: A survey.'' \textit{ACM Computing Surveys (CSUR)}, vol. 38, no. 4, 2006.

\bibitem[PNL]{PNL}Kalal Z., Matas J., Mikolajczyk K., ``P-N learning: Bootstrapping binary classifiers by structural constraints.'', \textit{2010 IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, pages 49-56. IEEE, June 2010.

\bibitem[ODS]{ODS} Prasad D.K., ``Survey of The Problem of Object Detection In Real Images.'', \textit{In International Journal of Image Processing (IJIP)}, Volume (6) : Issue (6), pages 441-466, 2012.

\bibitem[STV]{STV} B. D. Lucas and T. Kanade, ``An iterative image registration technique with an application to stereo vision.'', \textit{International Joint Conference on Artificial Intelligence}, vol. 81, pp. 674-679, 1981.

\bibitem[GFT]{GFT} Shi J., Tomasi C., ``Good features to track.'', \textit{Conference on Computer Vision and Pattern Recognition}, 1994.

\bibitem[KBT]{KBT} Comaniciu D., Ramesh V., Meer P., ``Kernel-Based Object Tracking.'',\textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 25, no. 5, pp. 564-577, 2003.

\bibitem[TUP]{TUP} Matthews I., Ishikawa T., Baker S., ``The Template Update Problem.'',\textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 26, no. 6, pp. 810-815, 2004.

\bibitem[SMAT]{SMAT} Dowson N, Bowden R., ``Simultaneous Modeling and Tracking (SMAT) of Feature Sets.'',\textit{Conference on Computer Vision and Pattern Recognition}, 2005.

\bibitem[RDT]{RDT} Rahimi A., Morency L. P., Darrell T., ``Reducing drift in differential tracking.'', \textit{Computer Vision and Image Understanding}, vol. 109, no. 2, pp. 97-111, 2008.

\bibitem[ROAM]{ROAM} Jepson A.D., Fleet D.J., El-Maraghi T. F.,``Robust Online Appearance Models for Visual Tracking'', \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}, pp. 1296-1311, 2003.

\bibitem[RFT]{RFT}Adam A., Rivlin E., Shimshoni I., ``Robust Fragments-based Tracking using the Integral Histogram.'',\textit{Conference on Computer Vision and Pattern Recognition}, pp. 798-805, 2006.

\bibitem[ETR]{ETR} Black M., Jepson A.D., ``Eigentracking: Robust matching and tracking of articulated objects using a view-based representation.'',\textit{International Journal of Computer Vision}, vol. 26, no. 1, pp. 63\textendash{}84, 1998.

\bibitem[RVT]{RVT} Ross D., Lim J., Lin R., Yang M., ``Incremental Learning for Robust Visual Tracking.'', \text{International Journal of Computer Vision}, vol. 77, pp. 125\textendash{}141, Aug. 2007.

\bibitem[VTD]{VTD} Kwon J., Lee K. M., ``Visual Tracking Decomposition.'', \textit{Conference on Computer Vision and Pattern Recognition}, 2010.

\bibitem[ONS]{ONS} Collins R., Liu Y., Leordeanu M., ``Online Selection of Discriminative Tracking Features.'', \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 27, no. 10, pp. 1631\textendash{}1643, 2005.

\bibitem[ENT]{ENT} Avidan S., ``Ensemble Tracking.'', \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 29, no. 2, pp. 261-271, 2007.

\bibitem[OBT]{OBT} Grabner H., Bischof H., ``On-line boosting and vision.'', \textit{Conference on Computer Vision and Pattern Recognition}, 2006.

\bibitem[MIP]{MIP} Sonka M, Fitzpatrick J.M., ``Handbook of Medical Imaging : Medical Image Processing and Analysis'' Volume 2

\bibitem[LCD]{LCD} Tseng D.-C., I-Ling Chung, Pei-Lin Tsai, Chang-Min Chou, ``Defect classification for LCD color filters using neural network-based decision tree classifier.'',\textit{ International Journal of Innovative Computing, Information and Control}, vol.7, no.7 (A), pp.3695-3707, 2011.

\bibitem[PED]{PED} Benenson R., Mathias M., Timofte R., Gool L.V., ``Pedestrian detection at 100 frames per second.'', \textit{Proc. IEEE Intl Conf. on Computer Vision and Pattern Recognition}, pp. 2903\textendash{}2910, 2012.

\bibitem[OCW]{OCW}http://opencv.org/platforms/cuda.html, 29.09.2013

\bibitem[FPIS]{FPIS} Sethi I., Jain R., ``Finding trajectories of feature points in a monocular image sequence.'' \textit{IEEE Trans. Patt. Analy. Mach. Intell. 9}, 1, 56-73, 1987

\bibitem[KAF]{KAF} Kalman R. E., ``A New Approach to Linear Filtering and Prediction Problems.'', \textit{Transactions of the ASME--Journal of Basic Engineering}, Vol 82, Series D, pp. 35 - 45, 1960

\bibitem[PAF]{PAF} Gordon N.J., Salmond D.J., Smith A.F.M., ``Novel approach to nonlinear/non-Gaussian Bayesian state estimation.'' \textit{IEE-Proceedings-F}, 140 , 107 - 113, 1993

\bibitem[INT]{INT} Schweitzer H., Bell J.W., WU F. 2002. ``Very fast template matching.'' \textit{In European Conference on Computer Vision (ECCV)}. 358 - 372.

\bibitem[LKT]{LKT} Tomasi C., Kanade T., ``Detection and Tracking of Point Features.'' \textit{Carnegie Mellon University Technical Report CMU-CS-91-132}, April 1991.

\bibitem[BSGF]{BSGF} Klein D.A., Cremers A.B., ``Boosting Scalable Gradient Features for Adaptive Real-Time Tracking'',\textit{IEEE Int. Conf. on Robotics and Automation (ICRA)}, pp. 4411-4416, May 2011

\bibitem[AVT]{AVT} Klein D. A., Schulz D., Frintrop S., Cremers A. B., ``Adaptive Real-Time Video-Tracking for Arbitrary Objects.'', \textit{IEEE Int. Conf. on Intelligent Robots and Systems (IROS)}, pp. 772-777, October 2010

\bibitem[OAN]{OAN} Morevec H. P.,``Towards Automatic Visual Obstacle Avoidance.'' \textit{Proceedings of the 5th international joint conference on Artificial intelligence} - Volume 2, pp. 584-584, 1977.

\bibitem[FOD]{FOD} Förstner W., Gülch E., ``A fast operator for detection and precise location of distinct points, corners and centres of circular features'', \textit{Proc. ISPRS Intercommission Workshop},pp. 149–155, 1987.

\bibitem[BAG]{BAG} Piccardi M., ``Background subtraction techniques: a review.'', \textit{IEEE International Conference on Systems, Man and Cybernetics 4}. pp. 3099–3104, 2004.

\bibitem[IMF]{IMF} Lowe D. G., ``Distinctive image features from scale-invariant keypoints.'', \textit{International Journal of Computer Vision}, vol. 60, no. 2, pp. 91–110, 2004.

\bibitem[MTL]{MTL} Taylor S., Drummond T., ``Multiple target localisation at over 100 fps'', \textit{British Machine Vision Conference}, 2009.

\bibitem[VAH]{VAH} Pilet J.,Saito H., ``Virtually augmenting hundreds of real pictures: An approach based on learning, retrieval, and tracking.'', \textit{2010 IEEE Virtual Reality Conference (VR)}, pp. 71–78, Mar. 2010.

\bibitem[SLI]{SLI} S. Obdrzalek and J. Matas, ``Sub-linear indexing for large scale object recognition.'', \textit{British Machine Vision Conference}, vol. 1, pp. 1–10, 2005.

\bibitem[CLU]{CLU} A. Blumand, T.Mitchell. ``Combining labeled and unlabeled data with co-training.'' \textit{COLT}, 1998.

\bibitem[TCL]{TCL} K. Nigam, A. McCallum, S. Thrun, and T. Mitchell. ``Text classification from labeled and unlabeled documents using EM.'', \textit{Machine learning}, 39(2):103–134, 2000.

\bibitem[TNO]{TNO} Huttenlocher D.P., Noh J.J., Ricklidge W.J., ``Tracking non-rigid objects on complex scenes'', in \textit{Computer Vision, 1993. Proceedings., Fourth Internation Conference}, 1993, pp. 93-101.

\bibitem[DMS]{DMS} Zhang T., Freedman D., ``Tracking objects using density matching and shape priors'', \textit{Preceedings of the Ninth IEEEE Interantion Conference on Comupter Vision}, pp. 1950-1954, 2003.

\bibitem[TGC]{TGC} Malcolm J.G., Rathi Y., Tannenbaum A.R., ``Tracking through clutter using graph cuts'', \textit{Britisch Maschine Vision Conference}, 2007.

\end{thebibliography}